Creating importance plot

### 2020-05-22 Scripts_for_results/03_creating_annotation_specifc_barplots.Rmd
fixed colors

>>>>

## SpectralTAD

#### 25kb

```{r}
badata_gm12878_25kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_spectralTAD_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_spectralTAD.rds"))
    perfdata <- perfdata[[3]]
  }

  badata_gm12878_25kb <- rbind(badata_gm12878_25kb,
                               perfdata[10,2])

```{r}
all_rfperfs <- data.frame(Perf=badata_gm12878_25kb)
all_rfperfs$Resolution <- rep("25 kb", length(badata_gm12878_25kb))
all_rfperfs$Annotation <- c("BroadHMM","HM","TFBS","ALL")
all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "BroadHMM", "TFBS", "ALL"))
all_rfperfs$Chromosome <- c(rep("CHR1", 4),
                            rep("CHR2", 4),
                            rep("CHR3", 4),
                            rep("CHR4", 4),
                            rep("CHR5", 4),
                            rep("CHR6", 4),
                            rep("CHR7", 4),
                            rep("CHR8", 4),
                            rep("CHR10", 4),
                            rep("CHR11", 4),
                            rep("CHR12", 4),
                            rep("CHR13", 4),
                            rep("CHR14", 4),
                            rep("CHR15", 4),
                            rep("CHR16", 4),
                            rep("CHR17", 4),
                            rep("CHR18", 4),
                            rep("CHR19", 4),
                            rep("CHR20", 4),
                            rep("CHR21", 4),
                            rep("CHR22", 4))

#### 25kb

```{r}
badata_k562_25kb <- numeric()
for(i in paste0("CHR", c(1:8,10:22))){
 for(j in c("BroadHMM", "HistoneModifications", "TFBS", "all")){
   print(c(i,j))
  if(j %in% c("BroadHMM", "HistoneModifications", "TFBS")){
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_spectralTAD_",
                               j, 
                               ".rds"))
    perfdata <- perfdata[[3]]
  }else{
    perfdata <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
                               i,
                               "/rus/distance/TADRF_spectralTAD.rds"))
    perfdata <- perfdata[[3]]
  }

  badata_k562_25kb <- rbind(badata_k562_25kb,
                               perfdata[10,2])

```{r}
all_rfperfs <- data.frame(Perf=badata_k562_25kb)
all_rfperfs$Resolution <- rep("10 kb", length(badata_k562_25kb))
all_rfperfs$Annotation <- c("BroadHMM","HM","TFBS","ALL")
all_rfperfs$Annotation <- factor(all_rfperfs$Annotation, levels = c("HM", "BroadHMM", "TFBS", "ALL"))
all_rfperfs$Chromosome <- c(rep("CHR1", 4),
                            rep("CHR2", 4),
                            rep("CHR3", 4),
                            rep("CHR4", 4),
                            rep("CHR5", 4),
                            rep("CHR6", 4),
                            rep("CHR7", 4),
                            rep("CHR8", 4),
                            rep("CHR10", 4),
                            rep("CHR11", 4),
                            rep("CHR12", 4),
                            rep("CHR13", 4),
                            rep("CHR14", 4),
                            rep("CHR15", 4),
                            rep("CHR16", 4),
                            rep("CHR17", 4),
                            rep("CHR18", 4),
                            rep("CHR19", 4),
                            rep("CHR20", 4),
                            rep("CHR21", 4),
                            rep("CHR22", 4))

### 2020-05-22 Scripts_for_results/04_creating_rfe_lineplot.Rmd
fixed colors

>>>>

## SpectralTAD

#### Optimal parameters: 25 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "25kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_spectralTAD.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,4:5)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}
rfeperchr$BA <- (rfeperchr$Sens+rfeperchr$Spec)/2
rfeperchr_summ <- rfeperchr %>%
  dplyr::group_by(Variables) %>%
  dplyr::summarise(Performance = mean(BA, na.rm = TRUE),
                   PerformanceSD = sd(BA, na.rm = TRUE))

#### Optimal parameters: 25 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("K562")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "25kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_spectralTAD.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

### 2020-05-22 Scripts_for_results/05_creating_importance_plot.Rmd
fixed colors

@@

>>>>

#### Optimal parameters: 10 kb, TFBS, distance type predictors, RUS

@@

## SpectralTAD

#### Optimal parameters: 25 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "25kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_spectralTAD.rds"))

#### Optimal parameters: 25 kb, TFBS, distance type predictors, RUS

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- list()
for(i in c("K562")){
  for(k in 1:length(chrs)){
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "25kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_spectralTAD.rds"))
